Resiliencia de *Quercus pyreancia* a dos eventos de sequía

### 2017-11-07 pres/state_ms.Rmd
clear pres
remove error checkout

---
title: "Resiliencia de *Quercus pyreancia* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output:
  rmdshower::shower_presentation:
    self_contained: false
    katex: true
    ratio: 16x10
---

@@

## Introduccion

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

@@

```{r pressure, echo=FALSE}
plot(pressure)
```

>>>>

---
title: "Resiliencia de *Quercus pyreancia* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output: 
  beamer_presentation
bibliography: ../references.bib
csl: ../nature.csl
---

@@

# Introduccion

- Item 1 
    - sub

---

# Sequía

- Aumento en la **severidad** y **frecuencia** de los eventos de sequías en las últimas décadas, especialmente para el sur de Europa [@VicenteSerrano2014; @Spinoni2015; @Stagge2017]
- Eventos extremos P. Ibérica: 1981, 1995, 2000, **2005**, **2012**  [@GarciaHerrera2007; @Gouveia2015; @Trigo2013]

## Análisis adicionales

- SPEI (Standardised Precipitation-Evapotranspiration Index) para datos

---

Sequía (análisis adicionales): SPEI

- Escala regional: exploramos la sequía a escala regional utilizando datos del [SPEI Global Drought Monitor](http://sac.csic.es/spei/database.html) para Sierra Nevada (spatial resolution of 0.5º) Ver [esto](https://github.com/ajpelu/qpyr_resilience/blob/master/analysis/drought/explore_drought_spei_regional.md):

@@
